### 2018-07-05 submission/manuscript.Rmd
update supplemental with gc table

***16S rRNA gene sequencing counts do not differ by GC content:*** Although the 16S rRNA gene sequencing counts varied by polymerase used, there was no difference between V4 16S rRNA genes with high and low GC content at every amplification cycle [Figure 1 & Table S1]. Additionally, there was also no difference in 16S rRNA gene sequencing counts between high and low GC content genomes [Table S2].

>>>>

***16S rRNA gene sequencing counts differ by GC content:*** There was a significant difference in relative abundance between high/low GC content based on either the V4 16S rRNA gene region or the whole genome [Figure 1, Table S1 & S2].

### 2018-07-05 submission/supplemental.Rmd
change title
update supplemental with gc table

# Error Introduced into 16S rRNA Gene Sequencing Results Varies by High Fidelity DNA Polymerase Used

@@

**Table S1: ANOVA results of differences in number of OTUs between polymerases in fecal and mock samples**

@@

@@

**Table S2: Tukey post-hoc results of differences in number of OTUs between polymerases in fecal and mock samples**

```{r supplemental_table2, echo=FALSE, message=FALSE, warning=FALSE}

@@

**Table S3: Kruskal-Wallis results of differences in error rate, sequences with an error, and chimera prevalence between polymerases in mock samples**

@@

**Table S4: Dunn's Post-Hoc results of differences in error rate, sequences with an error, and chimera prevalence between polymerases in mock samples**

>>>>

# Assessing the Differences in 16S rRNA Gene Sequencing Due to High Fidelity DNA Polymerase

@@

**Table S1: Wilcoxson Rank Sum Results of High versus Low GC groups based on the median percent of the V4 hypervariable region or the whole genome**

@@

mock_gc_wlcox <- as.data.frame(read_csv("../data/process/tables/v4_gc_wilcox_test_summary.csv")) %>% 
  arrange(p.value) %>% 
  mutate_at(vars(statistic), funs(round(., digits = 2))) %>% 
  mutate_at(vars(p.value:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  mutate(test_type = "V4 Region") %>% 
  bind_rows(
    as.data.frame(
    read_csv("../data/process/tables/whole_genome_gc_wilcox_test_summary.csv")) %>% 
    arrange(p.value) %>% 
    mutate_at(vars(statistic), funs(round(., digits = 2))) %>% 
    mutate_at(vars(p.value:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
    mutate(test_type = "Whole Genome")) %>% 
  select(cycles, taq, statistic, p.value, bh, test_type) %>% 
  filter(cycles != "fifteen") %>% 
  mutate(cycles = case_when(
    cycles == "twenty" ~ "20x", 
    cycles == "twenty_five" ~ "25x", 
    cycles == "thirty" ~ "30x", 
    cycles == "thirty_five" ~ "35x", 
    TRUE ~ "uh oh"))

colnames(mock_gc_wlcox) <- c("Number of Cycles", "Polymerase", "Rank Sum Statistic", "P-value", "BH", "Test Type")

kable(mock_gc_wlcox, format = "markdown", align = 'c', padding = 2)
```

**Table S2: ANOVA results of differences in number of OTUs between polymerases in fecal and mock samples**

```{r supplemental_table3, echo=FALSE, message=FALSE, warning=FALSE}

@@

**Table S3: Tukey post-hoc results of differences in number of OTUs between polymerases in fecal and mock samples**

```{r supplemental_table4, echo=FALSE, message=FALSE, warning=FALSE}

@@

**Table S4: Kruskal-Wallis results of differences in error rate, sequences with an error, and chimera prevalence between polymerases in mock samples**

@@

**Table S5: Dunn's Post-Hoc results of differences in error rate, sequences with an error, and chimera prevalence between polymerases in mock samples**
